Semistochastic importance sampling of second-quantized operators in determinant space

### 2021-06-04 notes/talk/talk.tex
Almost done with talk

\section{Motivation}
\begin{frame}{Types of quantum chemistry algorithms}
	\begin{enumerate}
		\item Orbital-space algorithms:
		\begin{enumerate}
			\item Coupled cluster
			\item Moller-Plesset perturbation theory
		\end{enumerate}
		\item Determinant-space algorithms:
		\begin{enumerate}
			\item Full CI
			\item Selected CI
			\item Epstein-Nesbet perturbation theory
			\item Full CI Quantum Monte Carlo (FCIQMC)
		\end{enumerate}
	\end{enumerate}
\end{frame}

@@

\begin{frame}
	\small
	In determinant-space algorithms, one of the key steps is applying a second-quantized operator (usually $H$) to a Slater determinant!
	\begin{enumerate}
		\item Full CI: Iterative diagonalization of the Hamiltonian (e.g. using Davidson) diagonalizes in the basis of Krylov vectors \begin{eqnarray}\{v_i=f(Hv_{i-1})\}\end{eqnarray}
		\item Selected CI: New determinants are `selected' using a criterion that is a function of $H\psi_0$
		\item Epstein-Nesbet perturbation theory: \begin{eqnarray}\Delta E = \left\langle \psi_0 \left| V \frac{1}{E_0 - H_0} V \right|\psi_0\right\rangle\end{eqnarray}
		\item FCIQMC: Stochastically simulate the power method, \begin{eqnarray}\psi_0 \propto \lim_{n\rightarrow\infty} (1 - \tau H)^n \psi_T\end{eqnarray}
	\end{enumerate}
\end{frame}

>>>>

\section{Motivation}
\begin{frame}{Types of quantum chemistry algorithms}
	\begin{enumerate}
		\item Orbital-space algorithms:
		\begin{enumerate}
			\item Coupled cluster
			\item Moller-Plesset perturbation theory
			\linebreak
		\end{enumerate}
		\item Determinant-space algorithms:
		\begin{enumerate}
			\item Full CI
			\item Selected CI
			\item Epstein-Nesbet perturbation theory
			\item Full CI Quantum Monte Carlo (FCIQMC)
		\end{enumerate}
	\end{enumerate}
\end{frame}

@@

\begin{frame}
	\small
	In determinant-space algorithms, one of the key steps is applying a second-quantized operator (usually $H$) to a Slater determinant!
	\begin{enumerate}
		\uncover<2->{\item Full CI: Iterative diagonalization of the Hamiltonian (e.g. using Davidson) diagonalizes in the basis of Krylov vectors \begin{eqnarray}\{v_i=f(Hv_{i-1})\}\end{eqnarray}}
		\uncover<3->{\item Selected CI: New determinants are `selected' using a criterion that is a function of $H\psi_0$}
		\uncover<4->{\item Epstein-Nesbet perturbation theory: \begin{eqnarray}\Delta E = \left\langle \psi_0 \left| V \frac{1}{E_0 - H_0} V \right|\psi_0\right\rangle\end{eqnarray}}
		\uncover<5->{\item FCIQMC: Stochastically simulate the power method, \begin{eqnarray}\psi_0 \propto \lim_{n\rightarrow\infty} (1 - \tau H)^n \psi_T\end{eqnarray}}
	\end{enumerate}
\end{frame}
